Effect of quality-adjusted production function inputs

### 2015-05-20 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Rearranged sections.

%++++++++++++++++++++++++++++++
\subsection{Dynamic Solow Residual} 
\label{sec:dynamic_solow_residual}
%++++++++++++++++++++++++++++++

This section presents results of dynamic Solow Residual analyses.

<<Dynamic Solow Residuals>>=
# Calculate finite difference approximations of time derivatives for output and all factors of production
lag <- 2       # Desired lag for calculations. Set to n for differences across n years.
pad <- "tail"  # Desired padding for NA values

@@

Figure~\ref{fig:DynamicSR_CD_Graph} shows the evolution 
of the Solow Residual~($\lambda$) over time
as calculated by Equation~\ref{eq:lambdaij} 
with timespan for finite differences set to 
\Sexpr{lag}~\Sexpr{if (lag == 1) "year" else "years"}.

<<DynamicSR_CD_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the Cobb-Douglas model.">>=
data <- filter(solowResiduals, model=="CD")
ggplot(data=data) +
  geom_line(mapping=aes(x=Year, y=lambda_fd, linetype=energy)) +
  scale_linetype_manual(values=c(2,3), name="") +
  facet_grid(Country ~ flavor) +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  xlab("") + 
  ylab(expression(lambda)) +
  xy_theme()
@

>>>>

%++++++++++++++++++++++++++++++
\subsection{Does quality-adjusting the factors of production 
            decrease the dynamic Solow residual?} 
\label{sec:quality_adj_energy_and_dynamic_solow_residual}
%++++++++++++++++++++++++++++++

<<Dynamic Solow Residuals>>=
# Calculate finite difference approximations of time derivatives for output and all factors of production
lag <- 3       # Desired lag for calculations. Set to n for differences across n years.
pad <- "tail"  # Desired padding for NA values

@@

Figure~\ref{fig:DynamicSR_CD_Graph} shows the evolution 
of the Solow residual~($\lambda$) over time
as calculated by Equation~\ref{eq:lambdaij} 
with the timespan for finite differences ($t_j - t_i$) set to 
\Sexpr{lag}~\Sexpr{if (lag == 1) "year" else "years"}.
It appears that quality-adjusting the factors of production
decreases the Solow residual~($\lambda$).

<<DynamicSR_CD_Graph, fig.pos="H", fig.align='center', fig.width=6.5, fig.height=4, fig.cap="Dynamic Solow residuals for the Cobb-Douglas model.">>=
data <- filter(solowResiduals, model=="CD")
ggplot(data=data) +
  geom_line(mapping=aes(x=Year, y=lambda_fd, linetype=energy)) +
  scale_linetype_manual(values=c(2,3), name="") +
  facet_grid(Country ~ flavor) +
  scale_x_continuous(breaks=c(1960, 1980, 2000)) +
  xlab("") + 
  ylab(expression(lambda[ij])) +
  xy_theme()
@
